---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r readmesetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![R-CMD-check](https://github.com/epiverse-trace/linelist/workflows/R-CMD-check/badge.svg)](https://github.com/epiverse-trace/linelist/actions)
[![codecov](https://codecov.io/gh/epiverse-trace/linelist/branch/main/graph/badge.svg?token=JGTCEY0W02)](https://codecov.io/gh/epiverse-trace/linelist)
<!-- badges: end -->

# Welcome to linelist!

<br>
**<span style="color: red;">NOTE</span>**

This package is a reboot of the RECON package
[linelist](https://github.com/reconhub/linelist). Unliked its predecessor, the
new package focuses on the implementation of a linelist class. It will also
eventually implement data cleaning tools, replicating functionalities of the
older package. However, the new package should be seen as a separate one, and
will not aim to be backward compatible due to its change in scope.


The development version of *linelist* can be installed from
[GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("epiverse-trace/linelist", build_vignettes = TRUE)
```

## linelist in a nutshell 

*linelist* is an R package which implements basic data representation for case
line lists, alongside accessors and basic methods. It relies on the idea that
key fields of the linelist such as dates of events (e.g. reporting, symptom
onset), age, gender, symptoms, outcome, or location, should be explicitely
identified to facilitate data cleaning, validation, and downstream analyses. 

A `linelist` object is an instance of a `data.frame` or a `tibble` in which key
epidemiological variables have been *tagged*. The main functions of the package
include:

* `make_linelist()`: to create a `linelist` object by tagging key epi variables in
  a `data.frame` or a `tibble`
  
* `tags()`: to list variables which have been tagged in a `linelist`

* `set_tags():` to modify tags in a `linelist`

* `select_tags():` to select columns of a `linelist` based on tags using *dplyr*
  compatible syntax
  
* `tags_df()`: to obtain a `data.frame` of all the tagged variables in a `linelist`

* `select()`: adapted from `dplyr::select`, for subsetting regular and tagged
  variables


## Worked example


## Contributing guidelines
Contributions are welcome via **pull requests**.

### Code of Conduct
Please note that the linelist project is released with a 
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

