---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r readmesetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![R-CMD-check](https://github.com/epiverse-trace/linelist/workflows/R-CMD-check/badge.svg)](https://github.com/epiverse-trace/linelist/actions)
[![codecov](https://codecov.io/gh/epiverse-trace/linelist/branch/main/graph/badge.svg?token=JGTCEY0W02)](https://codecov.io/gh/epiverse-trace/linelist)
<!-- badges: end -->

# Welcome to linelist!

<br>
**<span style="color: red;">NOTE</span>**

This package is a reboot of the RECON package
[linelist](https://github.com/reconhub/linelist). Unliked its predecessor, the
new package focuses on the implementation of a linelist class. It will also
eventually implement data cleaning tools, replicating functionalities of the
older package. However, the new package should be seen as a separate one, and
will not aim to be backward compatible due to its change in scope.


The development version of *linelist* can be installed from
[GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("epiverse-trace/linelist", build_vignettes = TRUE)
```

## linelist in a nutshell 

*linelist* is an R package which implements basic data representation for case
line lists, alongside accessors and basic methods. It relies on the idea that
key fields of the linelist such as dates of events (e.g. reporting, symptom
onset), age, gender, symptoms, outcome, or location, should be explicitely
identified to facilitate data cleaning, validation, and downstream analyses. 

A `linelist` object is an instance of a `data.frame` or a `tibble` in which key
epidemiological variables have been *tagged*. The main functions of the package
include:

* `make_linelist()`: to create a `linelist` object by tagging key epi variables in
  a `data.frame` or a `tibble`
  
* `tags()`: to list variables which have been tagged in a `linelist`

* `tags_names()`: to list all recognized tag names

* `set_tags():` to modify tags in a `linelist`

* `select_tags():` to select columns of a `linelist` based on tags using *dplyr*
  compatible syntax
  
* `tags_df()`: to obtain a `data.frame` of all the tagged variables in a `linelist`

* `select()`: adapted from `dplyr::select`, for subsetting regular and tagged
  variables


## Worked example

In this example, we use the case line list of the Hagelloch 1861 measles outbreak.

```{r }

# load libraries
library(outbreaks)
library(tibble)
library(dplyr)
library(magrittr)
library(linelist)

# overview of the data
measles_hagelloch_1861 %>%
  head()

```

Let us assume we want to tag the following variables to facilitate downstream
analyses:

* dates of onset, here called `prodrome`
* date of death
* age
* gender

Here, we will first create the outcome variable, then create a `linelist` with
the above information:

```{r }

x <- measles_hagelloch_1861 %>%
  tibble() %>%
  make_linelist(date_onset = "date_of_prodrome",
                date_death = "date_of_death",
                age = "age",
                gender = "gender")
x

```

The printing of the object confirms that the tags have been added. If we want to
double-check which variables have been tagged:

```{r }

tags(x)

```


Let us now assume we also want to record the outcome: it is currently missing
but can be built from dates of deaths (missing date = survived). This can be
done by using `mutate` to create the new variable, and setting up a new tag
using `set_tags`:

```{r }

x %>%
  mutate(inferred_outcome = if_else(is.na(date_of_death), "survided", "died")) %>%
  set_tags(outcome = "inferred_outcome")

```




## Contributing guidelines
Contributions are welcome via **pull requests**.

### Code of Conduct
Please note that the linelist project is released with a 
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

