---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r readmesetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/epiverse-trace/linelist/branch/master/graph/badge.svg)](https://codecov.io/gh/epiverse-trace/linelist?branch=master)
[![R-CMD-check](https://github.com/epiverse-trace/linelist/workflows/R-CMD-check/badge.svg)](https://github.com/epiverse-trace/linelist/actions)
<!-- badges: end -->

# Welcome to linelist!

<br>
**<span style="color: red;">NOTE</span>**

This package is a reboot of the RECON package
[linelist](https://github.com/reconhub/linelist). Unliked its predecessor, the
new package focuses on the implementation of a linelist class. It will also
eventually implement data cleaning tools, replicating functionalities of the
older package. However, the new package should be seen as a separate one, and
will not aim to be backward compatible due to its change in scope.


The development version of {linelist} can be installed from
[GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("epiverse-trace/linelist", build_vignettes = TRUE)
```

## linelist in a nutshell 

{linelist} is an R package which implements basic data representation for case
line lists, alongside accessors and basic methods. It relies on the idea that
key fields of the linelist such as dates of events (e.g. reporting, symptom
onset), age, gender, symptoms, outcome, or location, should be explicitely
identified to facilitate data cleaning, validation, and downstream analyses. 



## Contributing guidelines
Contributions are welcome via **pull requests**.

### Code of Conduct
Please note that the linelist project is released with a 
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

