---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r readmesetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->

[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![R-CMD-check](https://github.com/epiverse-trace/linelist/workflows/R-CMD-check/badge.svg)](https://github.com/epiverse-trace/linelist/actions)
[![codecov](https://codecov.io/gh/epiverse-trace/linelist/branch/main/graph/badge.svg?token=JGTCEY0W02)](https://codecov.io/gh/epiverse-trace/linelist)
[![lifecycle-experimental](https://raw.githubusercontent.com/reconverse/reconverse.github.io/master/images/badge-experimental.svg)](https://www.reconverse.org/lifecycle.html#experimental)

<!-- badges: end -->

# *linelist*: Tagging and Validating Epidemiological Data

<br>
**<span style="color: red;">NOTE</span>**

This package is a reboot of the RECON package
[linelist](https://github.com/reconhub/linelist). Unliked its predecessor, the
new package focuses on the implementation of a *linelist* class. The data
cleaning features of the original package will eventually be re-implemented for
*linelist* objects, albeit likely in a separate package.



## Installation

### Stable version

Our stable versions are released on CRAN, and can be installed using:

```{r, eval=FALSE}
install.packages("linelist", build_vignettes = TRUE)
```


### Development version

The development version of *linelist* can be installed from
[GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("epiverse-trace/linelist", build_vignettes = TRUE)
```



## Usage


## Documentation



## Getting help


## Contributions 

Contributions are welcome via **pull requests**.

### Code of Conduct
Please note that the linelist project is released with a 
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

